### 2018-04-16 experiments.tex
code

Using the original TSTL harness, approxoimately \emph{over 20\%} of all {\tt redis-py}
regression tests (of length 200) generated were flaky.  Using the
nondeterminism checker to reduce flaky tests to a minimal set allows
an engineer to leave an overnight run that will, in 12 hours, produce
a set of minimal flaky tests exposing the sources of
nondeterminism/flakiness.  In this case, the probability of flakiness
is not important, just the possibility, so we let the delta-debugging
create a minimal test with some non-zero (but possibly very small)
observed probability of nondeterminism.  The overhead for adding
nondeterminism checking is

@@

Moreover, turning off sources of expected nondeterminism makes
it possible to aggressively test {\tt redis-py} and Redis for
unexpected nondeterminism arising from actual bugs.  The overhead for such
determinism checks, with a 0 second delay between operations, is only
20\%, much lower than the expected cost of running each test twice.
This is because choosing the actions in a test (and determining which
actions are enabled at each step) consumes a large part of the test
generator's time; running the test again and checking equality is
relatively inexpensive.

@@

Removing the nondeterministic call, we can see that the cost of
checking for process nondeterminism, with a zero delay on operations,
is high, a 93\% slowdown.  This is due to the very high cost of
using a new subprocess to re-run the test, and comparing values using
text I/O on output pipes, rather than on values alone.

>>>>

Using the original TSTL harness, approxoimately \emph{over 20\%} of all {\tt redis-py}
regression tests (of length 200) generated were flaky.  Using the
nondeterminism checker to reduce flaky tests to a minimal set allows
an engineer to leave an overnight run that will, in 12 hours, produce
a set of minimal flaky tests exposing the sources of
nondeterminism/flakiness.  In this case, the probability of flakiness
is not important, just the possibility, so we let the delta-debugging
create a minimal test with some non-zero (but possibly very small)
observed probability of nondeterminism.

@@

Moreover, turning off sources of expected nondeterminism makes
it possible to aggressively test {\tt redis-py} and Redis for
unexpected nondeterminism arising from actual bugs.  The overhead for such
determinism checks, with no delay between operations, is only
20\%, much lower than the expected cost of running each test twice.
This is because choosing the actions in a test (and determining which
actions are enabled at each step) consumes a large part of the test
generator's time; running the test again and checking equality is
relatively inexpensive.

@@

Removing the nondeterministic call, we can see that the cost of
checking for process nondeterminism, with no delay between operations,
is high, a 93\% slowdown.  This is due to the very high cost of
using a new subprocess to re-run the test, and comparing values using
text I/O on output pipes, rather than on values alone.
